Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-04 paper-2024-sac-marl-neighbouring-strategies.tex
add caption figure 4

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/behavior.pdf}
  \caption{Graphical representation of wanted and unwanted behaviors.
  On the left, the wanted behavior, the agents correctly cooperate to cover
  two different items.
  While, on the right, the agents do not correctly cooperate covering
  the same item.
  }
  \label{fig:behavior}
\end{figure}

\section{Results and Evaluation}\label{sec:results}
\begin{itemize}
\item \textbf{Performance comparison:}
\begin{itemize}
\item Present the results of each distributed strategy against the centralized training baseline.
\item Use graphs and statistical analysis to compare the average episode length and average reward.
\item Highlight which neighbor-based methods perform comparably to centralized training.
\end{itemize}
\item \textbf{Scalability analysis:}
\begin{itemize}
\item Describe how the experiments were modified to assess scalability (increasing agents, spawn area).
\item Show how each method scales with the increasing complexity, using appropriate visualizations.
\item Discuss the implications of using pre-trained models with a larger number of agents.
\end{itemize}
\item \textbf{Communication overhead analysis:}
\begin{itemize}
\item Quantify the amount of information exchange for each strategy.
\item Compare the communication overhead across different neighborhood sizes, possibly using graphs.
\item Discuss the trade-offs between performance and communication efficiency.
\item Mention potential techniques for reducing communication overhead.
\end{itemize}
\end{itemize}

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/episode_reward_mean.pdf}
  \includegraphics[width=1\linewidth]{figures/episode_len_mean.pdf}
  \caption{Training results...}
  \label{fig:results}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/behavior.pdf}
  \caption{Wanted and unwanted behaviors.
  On the left, the wanted behavior, the agents correctly cooperate to cover
  two different items.
  While, on the right, the agents do not correctly cooperate covering
  the same item.
  }
  \label{fig:behavior}
\end{figure}

\section{Results and Evaluation}\label{sec:results}

% \begin{itemize}
% \item \textbf{Performance comparison:}
% \begin{itemize}
% \item Present the results of each distributed strategy against the centralized training baseline.
% \item Use graphs and statistical analysis to compare the average episode length and average reward.
% \item Highlight which neighbor-based methods perform comparably to centralized training.
% \end{itemize}
% \item \textbf{Scalability analysis:}
% \begin{itemize}
% \item Describe how the experiments were modified to assess scalability (increasing agents, spawn area).
% \item Show how each method scales with the increasing complexity, using appropriate visualizations.
% \item Discuss the implications of using pre-trained models with a larger number of agents.
% \end{itemize}
% \item \textbf{Communication overhead analysis:}
% \begin{itemize}
% \item Quantify the amount of information exchange for each strategy.
% \item Compare the communication overhead across different neighborhood sizes, possibly using graphs.
% \item Discuss the trade-offs between performance and communication efficiency.
% \item Mention potential techniques for reducing communication overhead.
% \end{itemize}
% \end{itemize}

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/episode_reward_mean.pdf}
  \includegraphics[width=1\linewidth]{figures/episode_len_mean.pdf}
  \caption{Data collected during training. 
  We can see that DTDE method is highly unstable, while neighbor-based strategies perform 
  comparably to CTDE.
  }
  \label{fig:results}
\end{figure}
